---
title: College Scorecard Database
format: gfm
---

Turn [College Scorecard data](https://collegescorecard.ed.gov/data/) into parquet files, a SQLite database, CSV and RDS (R data storage) files.

The code in this repository is licensed under [the MIT License](https://mit-license.org/). The data files are in the public domain.

## Dependencies and Setup

This project uses [renv](https://rstudio.github.io/renv) to manage dependencies. To install the dependencies, run `renv::restore()` in the R console on R 4.4.1.

```r
renv::restore()
```

## Instructions

We use [targets](https://docs.ropensci.org/targets/) to manage the data prep pipeline. To download the source data and build all outputs, run the following in the R console:

```r
targets::tar_make()
```

To update the data, invalidate the `url_data_zip` target -- `targets::tar_invalidate("url_data_zip")` -- and run `targets::tar_make()` again.

### Raw College Scorecard Data

The raw College Scorecard data is available as a set of parquet files in `data/parquet`. The complete scorecard dataset is stored as a set of parquet files in `` `r targets::tar_read("path_data_full_merged")` ``. Two informational tables contain the data dictionary (`` `r targets::tar_read("path_data_full_info")` ``) and the variable labels (`` `r targets::tar_read("path_data_full_labels")` ``) for categorical variables in the scorecard dataset.

```{r}
#| eval: false
scorecard <- targets::tar_read("path_data_full_merged") |> arrow::read_dataset()
dd_info   <- targets::tar_read("path_data_full_info")   |> arrow::read_parquet()
dd_labels <- targets::tar_read("path_data_full_labels") |> arrow::read_parquet()
```

### Tidy College Scorecard Tables

The most approachable tables are the `school_tidy` and `scorecard_tidy` targets.

```{r}
school_tidy <- targets::tar_read("school_tidy")
skimr::skim_tee(school_tidy)
```

```{r}
scorecard_tidy <- targets::tar_read("scorecard_tidy")
skimr::skim_tee(scorecard_tidy)
```

For ease of use, the variables in `school_tidy` and `scorecard_tidy` have been renamed from the original names. I don't yet have a mapping back to the original names, but you can reference the `data_dictionary` target to see information about the original names.

```{r}
data_dictionary <- targets::tar_read("data_dictionary")
head(data_dictionary$info, 10)
```
