---
title: College Scorecard Database
format: gfm
---

Turn [College Scorecard data](https://collegescorecard.ed.gov/data/) into parquet files, a SQLite database, CSV and RDS (R data storage) files.

License: GPL-3

## Dependencies and Setup

This project uses [renv](https://rstudio.github.io/renv) to manage dependencies. To install the dependencies, run `renv::restore()` in the R console on R 4.4.0.

```r
renv::restore()
```

## Instructions

We use [targets](https://docs.ropensci.org/targets/) to manage the data prep pipeline. To download the source data and build all outputs, run the following in the R console:

```r
targets::tar_make()
```

### Tidy College Scorecard Tables

The most approachable tables are the `school_tidy` and `scorecard_tidy` targets.

```{r}
school_tidy <- targets::tar_read("school_tidy")
skimr::skim_tee(school_tidy)
```

```{r}
scorecard_tidy <- targets::tar_read("scorecard_tidy")
skimr::skim_tee(scorecard_tidy)
```

For ease of use, the variables in `school_tidy` and `scorecard_tidy` have been renamed from the original names. I don't yet have a mapping back to the original names, but you can reference the `data_dictionary` target to see information about the original names.

```{r}
data_dictionary <- targets::tar_read("data_dictionary")
head(data_dictionary$info, 10)
```
