---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# collegeScorecard

<!-- badges: start -->
<!-- badges: end -->

collegeScorecard provides a tidied subset of the [US College Scorecard dataset](https://collegescorecard.ed.gov/data/), containing institutional characteristics, enrollment, student aid, costs, and student outcomes at institutions of higher education in the United States.

## Installation

Install collegeScorecard from CRAN with:

``` r
install.packages("collegeScorecard")
```

Or install the development version from r-universe

``` r
install.packages(
  "collegeScorecard",
  repos = c("https://gadenbuie.r-universe.dev", "https://cloud.r-project.org")
)
```

or from Github

``` r
# install.packages("pak")
pak::pak("gadenbuie/scorecard-db/pkg")
```

## Example

Loading collegeScorecard gives you access to `school` and `scorecard` tables, which are tibbles with information about institutions and yearly costs and admissions data, respectively.

```{r}
library(collegeScorecard)
```

```{r}
skimr::skim_tee(school)
```

```{r}
skimr::skim_tee(scorecard)
```

The help documentation of each dataset provides a short description of each column and the source of the data.
Additional information is included in the packaged data dictionary.

```{r}
readRDS(system.file("scorecard-data-dictionary.rds", package = "collegeScorecard"))
```
